### 2022-05-03 README.Rmd
add more notes for github pages
link to github *pages*
update README with project description

@@

@@

<!-- Consider using `targets::tar_github_actions()` if targets aren't too big -->

>>>>

The idea here is to investigate the consequences of including lagged effects (such as those modeled by distributed lag non-linear models) into population models (integral projection models, IPMs).
We'll compare population growth rates (lambda) with deterministic, stochastic (matrix shuffling), and lagged effects IPMs.

@@

[Notes for collaborators](https://brunalab.github.io/lagged-ipms/notes/index.html)

@@
